Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-07 talk/dls2012/paper.tex
add the final version of the code

If all the optimizations presented above are applied, the resulting
optimized peeled loop will consist of a single integer addition
only. That is it will become type-specialized to the types of the
variables \lstinline{step} and \lstinline{y}, and the overhead of
using boxed values is removed.

\revc{
This paper presents an elegant, if simple, technique, and demonstrates that
it's effective in small cases.  The worked example is particularly helpful, and
would be better if it were worked more thoroughly.  Some of the omitted steps
are not entirely obvious, and the paper would be improved by making the
clearer.  In particular, the final program presented on the bottom of page 5,
first column, still has memory access, boxing, and type checks, which the paper
then claims can be removed.  There's enough space to show this.
}
\cfbolz{
we have space now, can someone add the final optimized version of the loop?
}

>>>>

If all the optimizations presented above are applied, the resulting loop looks
as in Figure~\ref{fig:opt-trace}.
The resulting optimized peeled loop consists of a single integer addition
only. That is it will become type-specialized to the types of the
variables \lstinline{step} and \lstinline{y}, and the overhead of
using boxed values is removed.

\begin{figure}
\begin{lstlisting}[mathescape,numbers = right,basicstyle=\setstretch{1.05}\ttfamily\scriptsize]
$L_0$($p_{0}$, $p_{1}$):
# inside f: y = y.add(step)
guard_class($p_{1}$, BoxedInteger)
    # inside BoxedInteger.add
    $i_{2}$ = get($p_{1}$, intval)
    guard_class($p_{0}$, BoxedInteger)
        # inside BoxedInteger.add__int
        $i_{3}$ = get($p_{0}$, intval)
        $i_{4}$ = $i_{2}+i_{3}$
            # inside BoxedInteger.__init__
jump($L_1$, $p_{0}$, $i_{4}$)

$L_1$($p_{0}$, $i_{3}$, $i_{4}$):
    $i_{8}$ = $i_{4}+i_{3}$
jump($L_1$, $p_{0}$, $i_{3}$, $i_8$)
\end{lstlisting}
\caption{The fully optimized loop of the Example Interpreter}
\label{fig:opt-trace}
\end{figure}
